---
title: "Hand picking similar behaving group of customers to check clustering results"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
```


```{r read-data}
data <- read_rds("../../../data/elec_nogap_2013_100.rds")
quantile_prob_clust = seq(0.1, 0.9, 0.1)
quantile_prob_graph = c(0.25, 0.5, 0.75)
```

A clean dataset is obtained by choosing minimum sum of JS distances from each typical customer based on $quantiles = seq(0.1, 0.9, 0.1)$.
The objective is to see if the clustering algorithm then picks the least distant ones as the group.

## only hod

```{r clean-dataset}

# library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran(data, "hour_day", 
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_val)) %>% rename("dist_hod" = "dist")
# 
# 
# 
# v2 <- v2 %>% arrange(dist_hod) %>% filter(customer_from!=customer_to)
# 
# write_rds(v2, "../../../data/scaled_dist_nogap_2013_100.rds")
v2 <- read_rds("../../../data/scaled_dist_nogap_2013_100.rds")

data_pick_onepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8198401) %>% 
  arrange(dist_hod) %>% 
  head(n=5) 

data_pick_twopeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8181071) %>% 
  arrange(dist_hod) %>%
  head(n=5)
  
data_pick_threepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 11013154) %>% 
  arrange(dist_hod) %>% 
   head(n=5)

data_pick_cust <- bind_rows(
  c(data_pick_onepeak$customer_from, data_pick_onepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_twopeak$customer_from, data_pick_twopeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_threepeak$customer_from, data_pick_threepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"), .id = "design") %>% 
  filter(!(customer_id %in% c(8171227, 10183908)))
                       
data <- read_rds("../../../data/elec_nogap_2013_100.rds")

data_pick <- data %>% filter(customer_id %in% data_pick_cust$customer_id) %>% select(customer_id,reading_datetime, general_supply_kwh) %>% left_join(data_pick_cust)


write_csv(data_pick_cust, "../../../data/data_pick_cust_clean.rds")
```



```{r characterize-15cust, fig.cap= "Median (black) and quartile deviation (blue region) of hourly demand drawn for few customers showing similar behaviors. Roughly speaking, Design 1 has one evening peak, Design 2 has two peaks and Design 3 has three peaks in a day. Each of design 1, 2 and 3 have six similar behaving customers resulting to 18 time series. We want our clustering results to group each of the designs together."}

sm_hod <- gravitas::create_gran(data_pick, "hour_day")


sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(design, customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

  
ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- seq_len(nrow(sm_hod_list))


sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())


ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id, design))
  

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```
## Do they look similar on the transformed scale?

```{r transformed-scale}
data_pick_scaled <- data_pick %>%
    group_by(customer_id) %>%
    dplyr::mutate(general_supply_kwh =  stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x) %>%
    ungroup()

sm_hod <- gravitas::create_gran(data_pick_scaled, "hour_day")


sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(design, customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

  
ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- seq_len(nrow(sm_hod_list))


sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())


ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id, design))
  

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```


## only hod 
### Does hod as the only variable correctly identifies the groups?

```{r hod-only,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```


```{r clustering-result}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)


data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")
```


## hod + dom
### Is the clustering sensitive to nuisance parameter?


```{r hod-dom,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```


```{r clustering-result-hod-dom}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)




data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 5) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")
```

# All 100 customers
### Running it on all 100 and making 10 clusters. Do they have sufficiently different shapes?
### Variable importance

```{r hod-100cust,echo = TRUE}
# library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran(data, "hour_day", 
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")

#write_rds(v2, "../../../data/scaled_dist_100clust_deciles.rds")
v2 <- read_rds("../../../data/scaled_dist_100clust_deciles.rds")



data_dist <- v2 %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")


cust_ref <- bind_cols(customer_id=data_dist$customer_id, row = seq_len(nrow(data_dist)))

cust_rm_outlier <-   cust_ref %>% filter(!(row %in% c(73, 82, 79, 97, 25, 91)))

v3 <- v2%>% 
  filter(customer_from %in% cust_rm_outlier$customer_id,
         customer_to %in% cust_rm_outlier$customer_id)
    

data_dist <- v3 %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")




```


```{r hod-100cust-clustering}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

library(fpc)
# koptimal = fpc::nselectboot(as.dist(data_dist[,-1]),
#                         B = 5000,
#                         method = "ward.D",
#                         clustermethod = disthclustCBI, 
#                         classification = "averagedist",
#                         krange = 2:20)
# 
# koptimal = koptimal$kopt

groups <- tibble(group = cutree(hc, k=10), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())

data <- read_rds("../../../data/elec_nogap_2013_100.rds")
data <- data %>% left_join(groups) 

sm_hod <- gravitas::create_gran(data, "hour_day")

sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh, group) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)


ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- unique(sm_hod_list$group)

sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(group == group[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "group_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())


ref_cust <- unique(sm_hod_list$group) %>% as_tibble()%>% set_names("group")  %>% 
    mutate(group_serial_id = as.character(row_number()))
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(group_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>% 
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "group_serial_id") %>% 
  select(group_serial_id, categories_serial_id, category, everything())

# data_heatmap_100 <- sm_quantiles_ref %>% 
#  left_join(data %>% distinct(customer_id))
# 

sm_quantiles_ref$group = as.factor(sm_quantiles_ref$group)

sm_quantiles_ref %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(~group, 
             scales = "free_y", 
             labeller = "label_value") +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2") + scale_color_brewer(palette = "Dark2")
```
# Split these groups to see if the shapes of individual customers in a group is the same

```{r all100}
data <- read_rds("../../../data/elec_nogap_2013_100.rds")

sm_hod <- gravitas::create_gran(data, "hour_day")
sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)



ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- 1:100


sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())


ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>% 
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap_100 <- sm_quantiles_ref %>% 
 left_join(data %>% distinct(customer_id))

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==1) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-2")


data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==2) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-2")
#+   geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==3) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-3")
#+   geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==4) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-4")
#+ geom_smooth(size = 0.5, alpha = 0.5)


data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==5) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5)) +
  xlab("hour-day") +
  ggtitle("Group-5")
#+geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==6) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-6")
#+ geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==7) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-7")
#+  geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==8) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
    ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-8")
#+ geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==9) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
   ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-9")
#+geom_smooth(size = 0.5, alpha = 0.5)

data_heatmap_100 %>% 
  left_join(groups) %>% 
  filter(group==10) %>% 
  #filter(customer_id %in% c(8148781, 10703878)) %>% 
  ggplot(aes(x = as.integer(category))) +
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") + 
  geom_line(size = 0.5, aes(y = `50%`)) +
  facet_wrap(~customer_serial_id, scales = "free_y") + theme_minimal() + theme(strip.text.y = element_text(size = 5))+
  xlab("hour-day") +
  ggtitle("Group-10")
#+ geom_smooth(size = 0.5, alpha = 0.5) +
```






# Which variables are important for this clustering

I can do a ggpairs or parallel coordinate plot for this.
```{r}

data_pcp <- data_heatmap_100 %>% 
  left_join(groups)  %>% 
  select(customer_id, group, category, `50%`) %>% 
  mutate(category = as.factor(as.integer(category))) %>% 
  pivot_wider(names_from = category, values_from = `50%`) %>% 
  mutate(group = as.factor(group))



parcoord <- GGally::ggparcoord(data_pcp ,
                   columns = 3:ncol(data_pcp),
                   groupColumn = "group",
                   showPoints = FALSE, 
                   alphaLines = 0.8,
                   order = "allClass",
                   scale = "globalminmax"
) + ggplot2::theme_bw() +
  #scale_color_brewer(palette = "Dark2") + 
  ggplot2::theme(
    plot.title = ggplot2::element_text(size=10)
  )+
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 10)) +
  theme(legend.position = "bottom") +
  xlab("") +
  ylab("wpd") 

ggpairs_color <- ggscatmat(data_pcp, columns=3:ncol(data_pcp)) +
  scale_colour_brewer(palette="Set2") + theme(legend.position = "bottom")
parcoord
```

```{r}
ggpairs_color
```

```{r}
pc <- prcomp(data_pcp[c(-1,-2)], center = F, scale = F)
summary(pc)
# First two principal componentsafc
comp <- data.frame(pc$x[,1:2])
data_pcp_all <- data_pcp %>% bind_cols(comp)

library(RColorBrewer)
library(scales)
data_pcp_all %>% ggplot(aes(x=PC1, y = PC2)) + geom_point(aes(color = group)) +
  #scale_color_brewer(palette = "Dark2") +
   theme_bw() + theme(legend.position = "bottom")

```



# See if month_year works for your case
# Try with two granularities

