---
title: "Hand picking similar behaving group of customers to check clustering results"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE, cache = TRUE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
```


```{r read-data}
data1 <- read_rds("../../../data/elec_nogap_2013_500.rds")
data2 <- read_rds("../../../data/elec_nogap_2013_100.rds")
data3 <- data1 %>% bind_rows(data2 %>% filter(!(customer_id %in% data1$customer_id)))

write_rds(data3, "../../../data/elec_nogap_2013_600.rds")

quantile_prob_clust = seq(0.1, 0.9, 0.1)
quantile_prob_graph = c(0.25, 0.5, 0.75)
```

A clean dataset is obtained by choosing minimum sum of JS distances from each typical customer based on $quantiles = seq(0.1, 0.9, 0.1)$.
The objective is to see if the clustering algorithm then picks the least distant ones as the group.

## only hod

```{r clean-dataset}
library(gracsr)
# v2 <- suppressWarnings(
#   scaled_dist_gran(data3, "hour_day",
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
# 
# v2 <- v2 %>% arrange(dist_hod) %>% filter(customer_from!=customer_to)
# 
# write_rds(v2, "../../../data/scaled_dist_nogap_2013_600.rds")
# 
# data3 <- data3 %>% filter(!(customer_id %in% c(8143599)))
# 
# v3 <- suppressWarnings(
#   scaled_dist_gran_iqr(data3 %>% select(customer_id, reading_datetime, general_supply_kwh), "hour_day",
#                    response = "general_supply_kwh",
#                    quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
#   
# 
# v3 <- v3 %>% arrange(dist_hod) %>% filter(customer_from!=customer_to)
# 
# write_rds(v3, "../../../data/scaled_dist_nogap_2013_600_iqr.rds")

```

```{r}
v2 <- read_rds("../../../data/scaled_dist_nogap_2013_600.rds")

data_pick_onepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8198401) %>% 
  arrange(dist_hod) %>% 
  head(n=4) 

data_pick_twopeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8181071) %>% 
  arrange(dist_hod) %>%
  head(n=4)
  
11013154
data_pick_threepeak <- v2 %>% 
  arrange(dist_hod) %>%
  filter(customer_from == 8196501) %>% 
  arrange(dist_hod) %>% 
   head(n=4)

data_pick_cust <- bind_rows(
  c(data_pick_onepeak$customer_from, data_pick_onepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_twopeak$customer_from, data_pick_twopeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"),
                       c(data_pick_threepeak$customer_from, data_pick_threepeak$customer_to) %>% unique() %>% as_tibble() %>% set_names("customer_id"), .id = "design") %>%  filter(!(customer_id %in% c(8492316, 10346738, 8614285)))


# %>%  filter(!(customer_id %in% c(8171227, 10183908, 11013154, 8492316)))
                       
data <- read_rds("../../../data/elec_nogap_2013_600.rds")
data_pick <- data %>% filter(customer_id %in% data_pick_cust$customer_id) %>% select(customer_id,reading_datetime, general_supply_kwh) %>% left_join(data_pick_cust)

```



```{r characterize-15cust, fig.cap= "Median (black) and quartile deviation (blue region) of hourly demand drawn for few customers showing similar behaviors. Roughly speaking, Design 1 has one evening peak, Design 2 has two peaks and Design 3 has three peaks in a day. Each of design 1, 2 and 3 have six similar behaving customers resulting to 18 time series. We want our clustering results to group each of the designs together."}

sm_hod <- gravitas::create_gran(data_pick, "hour_day") 



sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(design, customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

  
ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- seq_len(nrow(sm_hod_list))


sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())

ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id, design))
  

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```

## Do they look similar on the transformed scale?

```{r transformed-scale}
data_pick_scaled <- data_pick %>%
    group_by(customer_id) %>%
    dplyr::mutate(general_supply_kwh =  stats::qqnorm(general_supply_kwh, plot.it=FALSE)$x) %>%
    ungroup()

sm_hod <- gravitas::create_gran(data_pick_scaled, "hour_day")


sm_hod_list <- sm_hod %>% 
  as_tibble() %>% 
  select(design, customer_id, hour_day, general_supply_kwh) %>% 
  pivot_wider(names_from = hour_day,
              values_from = general_supply_kwh)

  
ncol_sm <- seq_len(ncol(sm_hod_list[-c(1, 2)]))
nrow_sm <- seq_len(nrow(sm_hod_list))


sm_hod_quantiles_cat <- map(nrow_sm, function(x){
  map(ncol_sm, function(y){
   cell <- sm_hod_list%>% 
     dplyr::filter(customer_id == customer_id[x]) %>% 
     select(-c(1, 2)) %>% 
     extract(y) %>% 
     unlist()
   quantile(cell, prob = quantile_prob_graph)
})  %>% bind_rows(.id = "categories_serial_id")
}) %>% bind_rows(.id = "customer_serial_id") 


ref_cat <- names(sm_hod_list)[-c(1, 2)] %>% as_tibble() %>% set_names("category") %>%  
  mutate(categories_serial_id = row_number())


ref_cust <- sm_hod_list$customer_id %>% as_tibble()%>% set_names("customer_id")  %>% 
    mutate(customer_serial_id = row_number())
  
sm_quantiles_ref <- sm_hod_quantiles_cat %>% 
  mutate(customer_serial_id = as.integer(customer_serial_id),
         categories_serial_id = as.integer(categories_serial_id)) %>%
  left_join(ref_cat, by = "categories_serial_id") %>% 
  left_join(ref_cust, by = "customer_serial_id") %>% 
  select(customer_serial_id, categories_serial_id, category, customer_id, everything())

data_heatmap <- sm_quantiles_ref %>% 
 left_join(data_pick %>% distinct(customer_id, design))
  

data_heatmap %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`), size = 0.7) +
  facet_wrap(design~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)")
```


## Do they look similar on the robust transformed scale?

```{r robust-transformed}
data_scaled_robust <- robust_scale_data(data_pick, "hour_day")
suppressWarnings(plot_data(data_scaled_robust, "hour_day", response = "scaled_response", nfacet = 4))
```

## Does the method with NQT scaling identifies the groups? 

Yes it does.

```{r hod-only-nqt,echo = TRUE}
#quantile_prob_val = c(0.5, 0.75)
#data_pick <- data_pick %>% filter(!(customer_id %in% c(8485375, 8952846)))
library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod + dist_dom) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```


```{r clustering-result-nqt}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)


data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")
```


## Does the method with robust scalings identifies the groups? 

Yes it does.


```{r hod-only-robust,echo = TRUE}

library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran_iqr(data_pick, "hour_day", 
                   response = "general_supply_kwh",
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_hod" = "dist")
v3 <- suppressWarnings(
  scaled_dist_gran_iqr(data_pick, "day_month",
                   response = "general_supply_kwh", 
                   quantile_prob_val = quantile_prob_clust)) %>% rename("dist_dom" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  mutate(dist = dist_hod) %>% 
    pivot_wider(-c(3, 4), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")
```


```{r clustering-result-robust}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="ward.D")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
#groups %>% filter(group==1)
#groups %>% filter(group==2)
#groups %>% filter(group==3)


data_heatmap_new <- data_heatmap %>% left_join(groups)

data_heatmap_new$group = as.factor(data_heatmap_new$group)

data_heatmap_new %>% 
  ggplot(aes(x = as.integer(category))) + 
  geom_ribbon(aes(ymin = `25%`, 
                  ymax = `75%`), fill = "lightblue") +
  geom_line(aes(y = `50%`, color = group), size = 0.7) +
  facet_wrap(group~customer_id, 
             scales = "free_y", 
             labeller = "label_value",
             ncol = 4) +
  theme_bw() +
    theme(strip.text = element_text(size = 10, margin = margin(b = 0, t = 0))) + xlab("hour-of-day") + ylab("demand (in Kwh)") +
  scale_color_brewer(palette = "Dark2")
```

