---
title: "Selecting similar behaving group of customers to check clustering methodology"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, echo = FALSE, message=FALSE, warning=FALSE)
library(readr)
library(tidyverse)
library(gravitas)
library(tsibble)
library(parallel)
library(magrittr)
library(GGally)
library(knitr)
library(patchwork)
library(caret)
library(plotly)
library(gracsr)
library(here)
```

# Data

Consider customers for which moy, hod and wknd_wday are all harmonies from an initial sample of 600 customers which contained no missing values. Also consider customers for which the quantiles are of same value (to avoid problems in JS computation).

```{r}
elec_356_raw <- read_rds(here::here("data/elec_nogap_2013_clean_356cust.rds"))

elec_356_raw
```


# Classical MDS from distance metrics

```{r read-data}
# script to assimilate results from 02_algo1_moy_356cust_robust.R, 02_algo1_hod_356cust_robust.R and 02_algo1_wkndwday_356cust_robust.R
# write code after running the results for each of the above mentioned code

library(tidyverse)
library(gravitas)
library(tsibble)
library(ggpubr)

quantile_prob_graph <- c(0.25, 0.5, 0.75)

wkndwday <- read_rds(here("data/dist_gran_wkndwday_356cust_robust.rds"))

moy <- read_rds("../../../data/dist_gran_moy_356cust.rds")

hod <- read_rds("../../../data/dist_gran_hod_356cust_robust.rds") 

distance <- wkndwday %>% 
  left_join(moy, by = c("item1", "item2")) %>% 
  left_join(hod, by = c("item1", "item2")) %>% 
  rename("wkndwday" ="distance.x",
         "moy" = "distance.y",
         "hod" = "distance") %>%
  mutate(item1 = as.integer(as.character(item1)),
         item2 = as.integer(as.character(item2))) 

create_mds_gran <- function(total_distance){
  
total_distance_wide <- total_distance %>% pivot_wider(-c(2:5), 
                               names_from = item2,
                               values_from = total)

rownames(total_distance_wide) <- total_distance_wide$item1


#  changing to a lower traingular matrix as dist only takes lower traingular matrix (so in way tranposing it but tidyverse style, also creating a diagonal 0 with DM otherwise as.dist changing value)
mds_data <- total_distance_wide %>% 
  mutate_all(~replace(., is.na(.), 0)) %>%
   tibble::rownames_to_column() %>%  
   select(-item1) %>% 
   pivot_longer(-rowname) %>% 
   pivot_wider(names_from=rowname, values_from=value) 

df <- mds_data[-1] %>% as.matrix()
DM <- matrix(0, ncol(mds_data), ncol(mds_data))
DM[lower.tri(DM)] = df[lower.tri(df, diag=TRUE)]

f = as.dist(DM)

first_lot <- mds_data %>% names()
id <- c(first_lot[-1], mds_data$name[nrow(mds_data)])

mds  = cmdscale(f)
rownames(mds) = id
colnames(mds) = c("mds1", "mds2")

mds_hod <- bind_cols(mds, customer_id = id) 

mds_hod
 }

# for hod MDS scale

total_distance_hod <- distance %>% 
  mutate(total = hod) 

mds_hod <- create_mds_gran(total_distance_hod)

colnames(mds_hod) <- c("mds1.hod", "mds2.hod", "customer_id")

# for moy MDS scale

total_distance_moy <- distance %>% 
  mutate(total = moy)


mds_moy <- create_mds_gran(total_distance_moy)

colnames(mds_moy) <- c("mds1.moy", "mds2.moy", "customer_id")


# for wkndwday MDS scale

total_distance_wkndwday <- distance %>% 
  mutate(total = wkndwday)


mds_wkndwday <- create_mds_gran(total_distance_wkndwday)

colnames(mds_wkndwday) <- c("mds1.wkndwday", "mds2.wkndwday", "customer_id")


# for total MDS scale


total_distance_total <- distance %>% 
  mutate(total = wkndwday/2 + moy/12 + hod/24) 


mds_total <- create_mds_gran(total_distance_total)

colnames(mds_total) <- c("mds1.total", "mds2.total", "customer_id")


```


```{r wpd-mds}

## wpd

elec_356_raw <- read_rds(here::here("data/elec_nogap_2013_clean_356cust.rds"))

elec_600_wpd <- read_rds(here::here("data/algo2-cust600-wpd-rawdata.rds"))

elec_pick <- elec_600_wpd %>% 
  filter(customer_id %in% elec_356_raw$customer_id)

elec_pick_wide <- elec_pick %>% pivot_wider(-c(1, 2), names_from = "x_variable", values_from = wpd) 

mds <- elec_pick_wide[-1] %>% dist() %>% cmdscale() %>% as_tibble()

colnames(mds) <- c("mds1.wpd", "mds2.wpd")

mds_wpd <- bind_cols(mds, customer_id = elec_pick_wide$customer_id)%>% mutate(customer_id = as.character(customer_id))
```



```{r mds-all}
mds_all <- mds_hod %>% 
  left_join(mds_moy, by = "customer_id") %>% 
  left_join(mds_wkndwday, by = "customer_id") %>% 
  left_join(mds_total, by = "customer_id") %>% 
  left_join(mds_wpd, by = "customer_id") %>% 
  select(customer_id, everything())
```


# Visualize similarity between samples for different distance metrics hod+moy+wkndwday, hod, moy, wkndwday

```{r mds-all-2}

mds_tx <- highlight_key(mds_all, ~customer_id)

# initiate a plotly object
base <- plot_ly(mds_tx, color = I("black")) %>% 
  group_by(customer_id)

mds_hod <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.hod, y = ~ mds2.hod, text = ~customer_id)

mds_moy <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.moy, y = ~ mds2.moy, text = ~customer_id)

mds_wkndwday <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.wkndwday, y = ~ mds2.wkndwday, text = ~customer_id)

mds_total <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.total, y = ~ mds2.total, text = ~customer_id)

mds_wpd <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.wpd, y = ~ mds2.wpd, text = ~customer_id)


subplot(mds_total, mds_hod, mds_moy ,mds_wkndwday, titleX = TRUE) %>%
  layout(showlegend = FALSE) %>%
  highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect", persistent = TRUE)
            
            
            # defaultValues = c(8181071, 8184707, 8191495, 8269176, 8328008, 8454221, 8454235,  8598020, 8627007, 8636035, 8653709, 8659512, 8664102, 9345642, 9587992, 9822544, 10257830, 10357256, 10420689, 10582471, 10767756, 10909394, 11006388, 11013154)) 
```

# Visualize similarity between js and wpd methodologies:


```{r wpd-total}
subplot(mds_wpd, mds_total, nrows = 1, titleX = TRUE) %>%
  layout(showlegend = FALSE) %>%
  highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = 0.2, off = "plotly_deselect")
```



## --- Total 

```{r interactive-characterization}

quantile_hod <- quantile_gran(elec_356_raw, gran1 = "hour_day", quantile_prob_val = quantile_prob_graph)

quantile_hod$category <- factor(quantile_hod$category, levels = 0:23)

quantile_moy <- quantile_gran(elec_356_raw, gran1 = "month_year", quantile_prob_val = quantile_prob_graph)

  
quantile_moy$category <- factor(quantile_moy$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


quantile_wkndwday <- quantile_gran(elec_356_raw, gran1 = "wknd_wday", quantile_prob_val = quantile_prob_graph)

  
quantile_wkndwday$category <- factor(quantile_wkndwday$category, levels = c("Weekday", "Weekend"))


quantile_data <- bind_rows(quantile_hod, quantile_moy, quantile_wkndwday)


elec_pick_wide <- elec_pick %>% pivot_wider(c(3:5), names_from = "x_variable", values_from = wpd)


data_heatmap <- quantile_data %>% 
 left_join(elec_pick_wide) %>% 
  mutate(customer_id = as.character(customer_id))


# %>% 
#   mutate(categories_serial_id = as.factor(categories_serial_id)) %>% 
#   mutate(customer_id = as.character(customer_id))

data_heatmap_new <- data_heatmap %>%
left_join(mds_all, by = "customer_id") %>% 
  pivot_wider( names_from = quantiles, 
               values_from = quantiles_values) 
  

tx <- highlight_key(data_heatmap_new,
                    ~customer_id)

 # initiate a plotly object
 base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)
#
 quantile_plot <- base %>% 
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   add_ribbons(x = ~category,
               ymin = ~`25%`,
               ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)
 
mds_total <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.total, y = ~ mds2.total, text = ~customer_id)

mds_wpd <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.wpd, y = ~ mds2.wpd, text = ~customer_id)

 
subplot(mds_total, quantile_plot, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect", persistent = TRUE)
```



# hod


```{r}
data_heatmap_hod <- data_heatmap_new %>% 
  filter(gran == "hour_day") %>% 
  mutate(category = as.integer(category))

data_heatmap_hod$category <- factor(data_heatmap_hod$category, levels = 0:23)

tx <- highlight_key(data_heatmap_hod, ~customer_id) 


 # initiate a plotly object
base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)

 quantile_plot <- base %>%
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   add_ribbons(x = ~category,
             ymin = ~`25%`,
             ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)
 
 
 mds_hod <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.hod, y = ~ mds2.hod, text = ~customer_id)

subplot(mds_hod, quantile_plot, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect", persistent = TRUE)
# 

```

# moy

```{r}

data_heatmap_moy <- data_heatmap_new %>% 
  filter(gran == "month_year") 

  
data_heatmap_moy$category <- factor(data_heatmap_moy$category, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


#%>%  mutate(category = as.integer(category))

tx <- highlight_key(data_heatmap_moy, ~customer_id) 

 # initiate a plotly object
base <- plot_ly(tx, color = I("black")) %>%
   group_by(customer_id)

 quantile_plot <- base %>%
   group_by(customer_id, gran) %>%
   add_lines(x = ~ category, y = ~`50%`, color = ("black")) %>%
   add_ribbons(x = ~category,
             ymin = ~`25%`,
             ymax = ~`75%`, color = I("lightblue"), alpha = (0.5))%>%
   layout(showlegend = FALSE)
 
 
 mds_moy <- base %>%
  group_by(customer_id) %>%
  add_trace(x = ~mds1.moy, y = ~ mds2.moy, text = ~customer_id)

subplot(mds_moy, quantile_plot, widths = c(.6, .4), titleX = TRUE) %>% layout(showlegend = FALSE) %>% highlight(on = "plotly_selected", dynamic = TRUE, selectize = TRUE, selected = attrs_selected(0.5), opacityDim = .2, off = "plotly_deselect", persistent = TRUE)
```


## run upto this

