---
title: "Simulation with algorithm 2- different means and one nuisance granularity"
author: "Sayani Gupta"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,echo=FALSE, message=FALSE, warning = FALSE)
library(patchwork)
library(distributional)
library(ggplot2)
library(tidyverse)
library(knitr)
library(readr)
library(GGally)
library(tsibble)
library(gravitas)
```

# _Simulation design_

Three circular granularities g1, g2 and g3 are considered with levels 2, 3 and 4 respectively. Many time series with 600 observations are created using the four designs below, each of which is iterated five times. We anticipate to have four clusters, each with five time series conforming to the same design, once we execute the clustering. 

# _Algorithm_
Compute wpd for each granularity.The distance matrix is then computed with 20 time series as cases and three granularities as variables. Manhattan distances are computed and then hierarchical clustering is applied on them.


```{r}
t <- seq(0,299, 1)

g1 = rep(c(0, 1), length.out= length(t))
g1_dist_design1 <- rep(c(0, 0), length.out= length(t))
g1_dist_design2 <- rep(c(0, 2), length.out= length(t))
g1_dist_design3 <- rep(c(1, 4), length.out= length(t))
g1_dist_design4 <- rep(c(2, 4), length.out= length(t))

g2 = rep(c(0, 1, 2), length.out= length(t))
g2_dist_design1 <- rep(c(0, 0, 0), length.out= length(t))
g2_dist_design2 <- rep(c(1, 5, 7), length.out= length(t))
g2_dist_design3 <- rep(c(1, 2, 3), length.out= length(t))
g2_dist_design4 <- rep(c(0, 2, 4), length.out= length(t))


g3 = rep(c(0, 1, 2, 3), length.out= length(t))
g3_dist_design1 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design2 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design3 <- rep(c(0, 0, 0, 0), length.out= length(t))
g3_dist_design4 <- rep(c(0, 0, 0, 0), length.out= length(t))

time_series <- bind_rows(
  bind_cols(t, g1, g2, g3, g1_dist_design1, g2_dist_design1, g3_dist_design1),
  bind_cols(t, g1, g2, g3,  g1_dist_design2, g2_dist_design2, g3_dist_design2),
  bind_cols(t,  g1, g2, g3, g1_dist_design3, g2_dist_design3, g3_dist_design3),
  bind_cols(t,  g1, g2, g3, g1_dist_design4, g2_dist_design4, g3_dist_design4), .id = "design") %>%
  set_names(c("design", "t", "g1", "g2", "g3", "g1_dist", "g2_dist", "g3_dist")) %>% 
  mutate(sum_dist = g1_dist + g2_dist + g3_dist)

 time_series %>% group_by(design) %>% summarize(s = unique(sum_dist))
```



```{r}

generate_design <-  function (t = NULL, 
                           mu = NULL){
t <- seq(0, t, 1)
g1 <- t %%2
g2 <- t %%3
g3 <- t %%4

# design2 (change across g2 only)
mu = mu
len_mu <- length(mu)
len_obs <-  length(t)/length(mu)
dist <- dist_normal(mu = mu, sigma = 1)
numbers <- generate(dist, times = floor(len_obs))

timeseries <- numbers%>% 
  unlist() %>%
  matrix(ncol = len_mu, nrow = len_obs, byrow = FALSE) %>%
  t() %>% 
  matrix(ncol=1, byrow = TRUE)

timeseries <- as_tibble(timeseries) %>% 
  set_names("value") %>%
  bind_cols(t %>% as_tibble()) %>% 
  set_names(c("value", "t"))

 data <- tibble::tibble(t, g1, g2, g3) %>% left_join(timeseries)
 data
}

set.seed(12345)
data_design_1 <- generate_design(t = 299, mu = 0)
data_design_2 <- generate_design(t = 299, mu = c(1, 7, 7, 3, 5, 9))
data_design_3 <- generate_design(t = 299, mu = c(2, 6, 4, 5, 3, 7))
data_design_4 <- generate_design(t = 299, mu = c(2, 6, 6, 4, 4, 8))
```

<!-- # Design1 -->
```{r design-null, eval = FALSE}
p1 <- ggplot(data_design_1, aes(x = t, y = value)) + geom_line() + xlab("time")  + theme_bw() 
p2 <- ggplot(data_design_1, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw()
p3 <- ggplot(data_design_1, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw() 
p4 <- ggplot(data_design_1, aes(x = as.factor(g3), y = value)) + geom_boxplot() +
  xlab("g3") + theme_bw()

(p1 /(p2 + p3 + p4)) 
```

<!-- # Design2 -->
```{r design1, eval = FALSE}
p1 <- ggplot(data_design_2, aes(x = t, y = value)) + geom_line() + xlab("time")  + theme_bw()
p2 <- ggplot(data_design_2, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw()
p3 <- ggplot(data_design_2, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw()
p4 <- ggplot(data_design_2, aes(x = as.factor(g3), y = value)) + geom_boxplot() +
  xlab("g3") + theme_bw()

(p1 /(p2 + p3 + p4)) 
```

<!-- # Design3 -->

```{r design2, eval = FALSE}
p1 <- ggplot(data_design_3, aes(x = t, y = value)) + geom_line() + xlab("time")  + theme_bw()
p2 <- ggplot(data_design_3, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw()
p3 <- ggplot(data_design_3, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw()
p4 <- ggplot(data_design_3, aes(x = as.factor(g3), y = value)) + geom_boxplot() +
  xlab("g3") + theme_bw()

(p1 /(p2 + p3 + p4)) 
```

<!-- # Design4 -->

```{r design3, eval = FALSE}
p1 <- ggplot(data_design_4, aes(x = t, y = value)) + geom_line() + xlab("time")  + theme_bw()
p2 <- ggplot(data_design_4, aes(x = as.factor(g1), y = value)) + geom_boxplot() + xlab("g1") + theme_bw()
p3 <- ggplot(data_design_4, aes(x = as.factor(g2), y = value)) + geom_boxplot() + xlab("g2") + theme_bw()
p4 <- ggplot(data_design_4, aes(x = as.factor(g3), y = value)) + geom_boxplot() +
  xlab("g3") + theme_bw()

(p1 /(p2 + p3 + p4)) 

```


# Raw plots
```{r all-design}
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))

p1 <- ggplot(bind_data %>% filter(design!="design-2"), aes(x = t, y = value)) + geom_line() + xlab("time")  + theme_bw() + facet_wrap(~design, ncol = 1, scales = "free_y") + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0))) 
p2 <- ggplot(bind_data %>% filter(design!="design-2"), aes(x = as.factor(g1), y = value)) + geom_boxplot(width=0.5) + xlab("g1") + theme_bw() + facet_wrap(~design, ncol = 1, scales = "free_y") + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+stat_summary(fun.y = median, geom="line", group= 1, color= "blue", size = 0.5)
p3 <- ggplot(bind_data %>% filter(design!="design-2"), aes(x = as.factor(g2), y = value)) + geom_boxplot(width=0.5) + xlab("g2") + theme_bw() + facet_wrap(~design, ncol = 1, scales = "free_y") + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0)))+stat_summary(fun.y = median, geom="line", group= 1, color= "blue", size = 0.5)

p4 <- ggplot(bind_data %>% filter(design!="design-2"), aes(x = as.factor(g3), y = value)) + geom_boxplot(width=0.5) +
  xlab("g3") + theme_bw() + facet_wrap(~design, ncol = 1, scales = "free_y") + theme(
    strip.text = element_text(size = 8, margin = margin(b = 0, t = 0))) +stat_summary(fun.y = median, geom="line", group= 1, color= "blue", size = 0.5)

p1
```


# Designs (Distribution of simulated data across different granularities)

```{r, out.height="100%"}
(p2+p3+p4)

```


```{r}
seed_len = seq(12345, 12349, 1)
bind_data_iter <- map(seq_len(length(seed_len)), function(x){
set.seed(seed_len[x])
data_design_1 <- generate_design(t = 299, mu = 0)
data_design_2 <- generate_design(t = 299, mu = c(1, 7, 7, 3, 5, 9))
data_design_3 <- generate_design(t = 299, mu = c(2, 6, 4, 5, 3, 7))
data_design_4 <- generate_design(t = 299, mu = c(2, 6, 6, 4, 4, 8))
bind_data <- bind_rows(data_design_1, data_design_2, data_design_3, data_design_4, .id = "design") %>% mutate(design = paste("design", design, sep = "-"))
}) %>% bind_rows(.id = "seed_id")

```


```{r}

quantile_prob_val = seq(0.1,0.9,0.1)
bind_data_iter <- bind_data_iter %>% mutate(
  customer_id  = paste0(design,"-s-", seed_id)) %>%
   as_tsibble(key=customer_id,index=t) %>% 
  filter(design!="design-2")

library(gracsr)
v2 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g1", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val))%>% rename("dist_g1" = "dist")

v3 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g2", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_g2" = "dist")

v4 <- suppressWarnings(
  scaled_dist_gran(bind_data_iter, "g3", 
                   response = "value",
                   quantile_prob_val = quantile_prob_val)) %>% rename("dist_g3" = "dist")

data_dist <- v3 %>% 
  left_join(v2) %>%
  left_join(v4) %>% 
  mutate(dist = dist_g1 + dist_g2 +dist_g3) %>% 
    pivot_wider(-c(3, 4, 5), 
                names_from = customer_to,
              values_from = dist) %>%
  rename("customer_id" = "customer_from")

```

```{r groups}
d = stats::as.dist(data_dist[,-1])
hc = stats::hclust(d,method="complete")

groups <- tibble(group = cutree(hc, k=3), customer_id = data_dist$customer_id)
groups %>% group_by(group) %>% summarise(n=n())
groups %>% filter(group==1)
groups %>% filter(group==2)
groups %>% filter(group==3)
#groups %>% filter(group==4)
```

